---
title: "Showing off some ggplot2 skills"
author: "Yingfei Mu & Wenjing Bao"
date: </br>`r format(Sys.time(), '%d %B %Y')`
output: github_document
---

```{r setup, include=FALSE}
## These next lines set the default behaviour for all R chunks in the .Rmd document.
## I recomend you take a look here: https://rmarkdown.rstudio.com/authoring_rcodechunks.html
knitr::opts_chunk$set(echo = TRUE) ## Show all R output
knitr::opts_chunk$set(cache=TRUE) ## Cache the results to increase performance.
```

## Goal and requirements

The goal of this assignment is simple: I want you to produce *four* different figures using **ggplot2**. They don't have to be identify causal relationships, or anything like that. I just want you to stretch your visualization legs and demonstrate any new (or existing) **ggplot2** skills that you have acquired since our first lecture. 

Some additional points:

- You are free to use any dataset that comes in-built with base R, or bundled together with an external R package. See [here](https://vincentarelbundock.github.io/Rdatasets/datasets.html) for an impressive list.

- That being said, I would especially encourage you to use your own data. 
  - I know we haven't gotten to data importation yet, but take a look [here](https://support.rstudio.com/hc/en-us/articles/218611977-Importing-Data-with-RStudio) if you need help. I would recommend that you install the **readr**, **read_excel** and **haven** packages first, though.
  - If your dataset isn't proprietary (or isn't being read directly off the web), please save it in the (empty) `data/` folder of this repo. 

- You can use the same dataset for all four of your plots. Or you can use a new dataset for each plot. Regardless of what you choose, I want you to try and use different geoms for each figure.

- Any other **ggplot2** skills and add-ons like faceting, changing aesthetic scales or legends, using different themes (e.g. from the **ggthemes** package), animation, etc. are all welcome and encouraged.

- I want to *see* the code that produces the figures. (Don't use `echo=FALSE` in any of the code chunks, if that means anything to you.)

### What you will be graded on

- Are your figures clear? (e.g. lack of chart chunk, non-overlapping labels)
- Are your figures compelling? (e.g. use an appropriate geom for the insight that you want to convey)
- Variation (I don't want to see four line charts of the same dataset... Be creative)
- Did you read and follow my instructions (e.g. describe your data and figures, show the code that produced the figures, include data in the `/data` folder, etc)
- etc.

Lastly, don't forget to knit the assignment (click the "Knit" button, or press `Ctrl+Shift+K`) before submitting!

## Start the assignment

Here is a R code chunk for you to load your packages. Feel free to load as many other packages and insert as many additional code chunks (`Ctr+Alt+I`) as you need. You can always load additional packages in the their own chunk blocks, but I recommend loading all of your packages together at the top.)

```{r libs}
if (!require("pacman")) install.packages("pacman")
## Note: The `p_load()` function from the pacman package is a convenient way to 
## install (if necessary) and load packages all at once. You can think of this
## as an alternative to the normal `library(ggplot2); library(here);...` way of
## loading R packages.
pacman::p_load(ggplot2, here)
```


### Figure 1: Iris Species and Their Sepal Length

Load/read in the data. (Delete this chunk if you don't need it.)
```{r data1}
# library(readr)
# cool_data <- read_csv(here("data/my-cool-data.csv"))
data(iris)
str(iris)
summary(iris)
```

Briefly describe the data here. Then produce the figure.
There are five variables in this dataset, including species, petal width and length as well as sepal length and width. The Figure 1 tries to compare sepal length between different iris species. We also mapped species based on their sepal length and width to give a better visualization on where each species is.
```{r fig1}
# Plot code here
plot(iris$Species, iris$Sepal.Length, xlab="Species", ylab="Sepal Length", main="Iris Species and Their Sepal Length")
ggplot(data=iris, aes(x=Sepal.Width, y=Sepal.Length, col=Species))+geom_point()
```
From Figure 1, we can see virginica has the largest median sepal length while setosa has the smallest median sepal length, and there is an outlier in the virginica data. 

Finally, tell me what I am looking at. Point out anything that you think is of interest. Now do the same for Figs. 2-4 below...

### Figure 2: Sepal Length vs. Petal Length
For Figure 2, we try to find out the relationship between iris sepal length and petal length. From the regression line, we can see there is a positive correlation between iris petal length and sepal length.
```{r fig2}
# Plot code here
plot(iris$Sepal.Length ~ iris$Petal.Length,  xlab="Petal Length", ylab="Sepal Length", main="Sepal Length vs. Petal Length", col="pink", pch=16)
abline(lm(iris$Sepal.Length ~ iris$Petal.Length),  col="purple")
```

### Figure 3: Title description

```{r fig3}
# Plot code here
```

### Figure 4: Title description

```{r fig4}
# Plot code here
```
